Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/main_jfm.tex
type

\ReviewerThree{
The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
}
%

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
  \caption{\label{figure13} Comparisons between the proposed model and a conitnuum model in 
  two JP vesicle simulations. 
  $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
  the proposed model.}
\end{figure}

>>>>

\ReviewerThree{
The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
been shown to capture well the lubrication hydrodynamics in the narrow space between boundaries 
when the repulsive potential $P$ gives a large steric force \citep{qua-bir2014}.  
In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \citep{qua-vee-you2019,qua-gan-you2021}.
}
%

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model in 
  two JP vesicle simulations. 
  $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
  the proposed model.}
\end{figure}
